---
author: "grabowski pawel"
date: "Wednesday, March 11, 2015"
output: html_document
---


<h2>Differences between two TV Series</h2>

The aim of this exercise is to provide basic informations about 2 TV Series and see the ratings of every single episode given by **site** users.
The **site**  is *http://www.imdb.com/* which contain ratings/comments/basic info of every movie or TV Series.  The HTML site was parsed using **rvest** package, which is mainly used for parsing sites that doesn't have tabular form.

```{r, echo=FALSE, cache=TRUE}
suppressWarnings(library(rvest))
library(stringi)


tv_series_info <- function(url){
   stopifnot(is.character(url))
   
   ###parsing  HTML page
   html_basic_info <- html(url)
   
   ###basic info
   #title
   series_title <- html_nodes(html_basic_info, ".title-extra")
   series_title <- unlist(stri_extract_all_regex(html_text(series_title), '(?<=").+(?=")'))
   #genre
   series_genre <- html_nodes(html_basic_info, ".infobar .itemprop")
   series_genre <- stri_paste(html_text(series_genre), collapse = ', ')
   #grade
   series_grade <- html_nodes(html_basic_info, ".star-box-giga-star")
   series_grade <- as.numeric(html_text(series_grade))
   

   ###all episodes rated, sorted by date
   url_episodes <- stri_paste(url, "epdate")
   html_episodes <- html(url_episodes)
   #reading table into data frame with all episodes' info
   df_episodes <- html_nodes(html_episodes, "table")[[1]]
   df_episodes <- html_table(df_episodes)
   #lets divide first column into 2 separate columns, where 1 is season number and the latter is episode number
   temp_episodes_numbers <- as.numeric(unlist(stri_extract_all_regex(df_episodes[,1], "\\p{N}+")))
   odd_even <- rep(c(TRUE,FALSE), times=length(temp_episodes_numbers)/2)
   temp_season <- temp_episodes_numbers[odd_even]
   temp_episode <- temp_episodes_numbers[!odd_even]
   #delete first and last column from df_episodes since they are unnecesary and then cbind it with episode and season numbers 
   df_episodes <- cbind(temp_season, temp_episode, df_episodes[,2:4])
   #change names of columns
   names(df_episodes) <- c('Season','Episode','Title','Rating','Votes')
   
   
   
   ###ratings of TV series of male group
   html_ratings_male <- html(stri_paste(url, "ratings-male"))
   temp_male_rating <- html_nodes(html_ratings_male, "p+ table td ")
   temp_male_rating <-  html_text(temp_male_rating)
   temp_male_rating <- as.numeric(na.omit(unlist(stri_extract_all_regex(temp_male_rating, "\\p{N}{1,2}.\\p{N}{1,2}(?=%)"))))
   df_male_percentage_rating <- data.frame("Rating"=1:10, "Percentage"=rev(temp_male_rating))
   
   ###ratings of TV series of female group
   html_ratings_female <- html(stri_paste(url, "ratings-female"))
   temp_female_rating <- html_nodes(html_ratings_female, "p+ table td ")
   temp_female_rating <-  html_text(temp_female_rating)
   temp_female_rating <- as.numeric(na.omit(unlist(stri_extract_all_regex(temp_female_rating, "\\p{N}{1,2}.\\p{N}{1,2}(?=%)"))))
   df_female_percentage_rating <- data.frame("Rating"=1:10, "Percentage"=rev(temp_female_rating))
   
   ### ratings of both male and female(for dual barplot)
   df_both <- rbind(df_male_percentage_rating,df_female_percentage_rating)
   df_both <- cbind(df_both,rep(c('male','female'), each=10))
   names(df_both)[3] <- 'sex'
   res <-list(series_title, series_genre, series_grade, df_episodes, df_male_percentage_rating, df_female_percentage_rating, df_both)
   names(res) <- c('Title', 'Genre','Grade', 'Episodes', 'Male', 'Female', 'Both')
   return(res)
}

game_of_thrones <- "http://www.imdb.com/title/tt0944947/"
summary_game_of_thrones <- tv_series_info(game_of_thrones)

the_walking_dead <- "http://www.imdb.com/title/tt1520211/"
summary_the_walking_dead <- tv_series_info(the_walking_dead)
```

The first TV Series is **`r summary_game_of_thrones$Title`**, which belengs to  *`r summary_game_of_thrones$Genre`* cathegory and the overall grade is **`r summary_game_of_thrones$Grade`**.

Percentage distribution in **male** group:
```{r, echo=FALSE}
library(ggplot2)
ggplot(summary_game_of_thrones$Male,aes(x = factor(Rating), y = Percentage)) +
   geom_bar(stat="identity",fill='pink',colour="red") + xlab("Ratings")
```

Percentage distribution in **female** group:
```{r, echo=FALSE}
ggplot(summary_game_of_thrones$Male,aes(x = factor(Rating), y = Percentage)) +
   geom_bar(stat="identity",fill='pink',colour="red") + xlab("Ratings")
```

Percentage distribution in **both** groups:
```{r, echo=FALSE}

ggplot(summary_game_of_thrones$Both,aes(x = factor(Rating), y = Percentage, fill=sex)) +
   geom_bar(stat="identity", position="dodge") + xlab("Ratings") 
```

Rating for all the episodes:

```{r, echo=FALSE}
lengthx <- length(summary_game_of_thrones$Episodes[,4])
ggplot(summary_game_of_thrones$Episodes,aes(x=1:lengthx, y=Rating)) + geom_line() + xlab('Episode')
```

Average rating for every season:

```{r, echo=FALSE}
temp_ <- tapply(summary_game_of_thrones$Episodes[,4],summary_game_of_thrones$Episodes[,1],mean)
temp_x <- length(unique(summary_game_of_thrones$Episodes[,1]))
temp_df <- data.frame(y=temp_)
ggplot(data=temp_df , aes(x=1:temp_x, y=y)) + geom_line() + xlab('Season')
```


The second TV Series is **`r summary_the_walking_dead$Title`**,  which belengs to  *`r summary_the_walking_dead$Genre`* cathegory and the overall grade is **`r summary_the_walking_dead$Grade`**.

Percentage distribution in **male** group:
```{r, echo=FALSE}
library(ggplot2)
ggplot(summary_the_walking_dead$Male,aes(x = factor(Rating), y = Percentage)) +
   geom_bar(stat="identity",fill='pink',colour="red") + xlab("Ratings")
```

Percentage distribution in **female** group:
```{r, echo=FALSE}
ggplot(summary_the_walking_dead$Male,aes(x = factor(Rating), y = Percentage)) +
   geom_bar(stat="identity",fill='pink',colour="red") + xlab("Ratings")
```

Percentage distribution in **both** groups:
```{r, echo=FALSE}
library(ggplot2)
ggplot(summary_the_walking_dead$Both,aes(x = factor(Rating), y = Percentage, fill=sex)) +
   geom_bar(stat="identity",position="dodge") + xlab("Ratings") 
```

Rating for all the episodes:

```{r, echo=FALSE}
lengthx <- length(summary_the_walking_dead$Episodes[,4])
ggplot(summary_the_walking_dead$Episodes,aes(x=1:lengthx, y=Rating)) + geom_line() + xlab('Episode')
```

Average rating for every season:

```{r, echo=FALSE}
temp_ <- tapply(summary_the_walking_dead$Episodes[,4],summary_the_walking_dead$Episodes[,1],mean)
temp_x <- length(unique(summary_the_walking_dead$Episodes[,1]))
temp_df <- data.frame(y=temp_)
ggplot(data=temp_df , aes(x=1:temp_x, y=y)) + geom_line() + xlab('Season')
```
